Efficient Selection of Time Series Shapelets

### 2024-04-17 Docs/paper/main.tex
Learning shapelets

This paper~\cite{learning_shapelets} takes an alternative approach, where
instead of selecting shapelets it \emph{learns} non existing shapelets.
We should mention the evaluation measures~\cite{alternative_measures}.
We will use Silhouette~\cite{silhouettes} as motivation to exploit neighborhood
structure.

>>>>

While all the previous work found shapelets by extracting subsequences from the
time series, Grabocka et al.~\cite{learning_shapelets} take an alternative
approach, where instead of selecting shapelets, they \emph{learn} them by
solving an optimization problem.
